The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Add competition-wide score.

>>>>

\paragraph{Competition-Wide Score (\maintrack).}
A competition-wide metric for the main track, separately for
parallel and sequential performance, was defined as follows.

Let $N_i$ be the total number of benchmarks in division~$i$ that were used in the
competition (and not removed because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
raw score for this division.
%
In 2015 and 2016,
the \emph{competition-wide raw score} for a solver was defined as
%
$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$,
%
where the sum is over all competitive
divisions into which the solver was
entered.
%
In 2017, the (per-division) penalty for erroneous results was changed from the
number of errors to a fixed constant, since the weight already takes the number
of benchmarks in the division into account, and multiplying it by the number of
errors overemphasizes large divisions.
In 2017 and 2018,
the \emph{competition-wide raw score} for a solver was thus defined as
%
$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$,
%
where the sum is over all competitive divisions into which the solver
was entered.
